---
title: "Analysis"
subtitle: "[ReactExtMRI] Combining gPPI, SCR, and rating data"
author: "Emma Biggs"
date: "09/03/2026"

output:
  html_document:
    toc: true
    toc_float: true
    theme: united
    highlight: tango
    code_folding: hide
    df_print: paged

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

# Load libraries
library(tidyverse) # For data manipulation and ggplot2
library(DT)        # For interactive tables
library(bain)      # For Bayesian Informative Hypotheses Evaluation (JASP)
library(forcats)   # For re-ordering factors
library(emmeans)   # For calculating slopes
library(broom)     # For navigating stats tables
library(stringr)   # For renaming strings in column names

```

# Data preprocessing
- Import Ratings, SCR, and gPPI data
- Concatenate into one long form data file
- Save data file in ..data/processed/master_data.csv

*SCR data is averaged per phase, except for extinction where it is split into early (t1-6) and late (t7-12). Only late extinction is carried forward in the master data for further analysis*

*ID naming is corrected so that gPPI ID codes (1 - 29) map onto p001 - p030. No data for p012.*

```{r data_preprocess, message=FALSE, warning=FALSE}

# Load Data
ratings_raw <- read_csv("../data/raw/Ratings.csv")
scr_raw     <- read_csv("../data/raw/SCR.csv")

gppi_ext   <- read_csv("../data/raw/gPPI_EXT.csv") %>% mutate(Phase = "EXT")
gppi_extre <- read_csv("../data/raw/gPPI_EXTRE.csv") %>% mutate(Phase = "EXT-RE")
gppi_ren   <- read_csv("../data/raw/gPPI_REN.csv") %>% mutate(Phase = "REN")

gppi_all <- bind_rows(gppi_ext, gppi_extre, gppi_ren)

# Fix the ID codes for gPPI
# Create a map: 1-11 -> p001-p011, 12-29 -> p013-p030 (skipping p012 due to missing data)
id_lookup <- data.frame(
  gppi_id = 1:29,
  pID = c(sprintf("p%03d", 1:11), sprintf("p%03d", 13:30))
)

gppi_clean <- gppi_all %>%
  left_join(id_lookup, by = c("pID" = "gppi_id")) %>%
  select(-pID) %>% 
  rename(pID = pID.y) %>% # Clean up names
  rename_with(~ str_replace_all(.x, " ", "_"))

# Load dictionary for gPPI connection names
gppi_metadata <- read_csv("../data/raw/gPPI_metadata.csv") %>%
  mutate(
    Clean_Name = paste0(ROI1, "_to_", ROI2), # Create ROI1_to_ROI2 name
    Connection = str_replace_all(Connection, " ", "_") # Remove spaces from column names
  )
conn_dict <- setNames(gppi_metadata$Clean_Name, gppi_metadata$Connection)
cat_dict <- setNames(gppi_metadata$Category, gppi_metadata$Connection)
# Add entries for ratings and SCR
cat_dict["SCR"]    <- "Physiology" 
cat_dict["Rating"] <- "Self-report"

# Pivot Ratings to Long Format
ratings_long <- ratings_raw %>%
  pivot_longer(
    cols = -pID, 
    names_to = c("CS_Type", "Phase"), 
    names_sep = "_",
    values_to = "Rating"
  )

# Pivot SCR to Long (Handling Trial Numbers)
scr_long <- scr_raw %>%
  pivot_longer(
    cols = -pID,
    names_to = c("CS_Type", "Phase", "Trial"),
    names_pattern = "(.*)_(.*)_t(\\d+)",
    values_to = "SCR_Score"
  ) %>%
  mutate(
    Trial = as.numeric(Trial), # Ensure trial is a number
    CS_Type = case_match(CS_Type,
      "CSplusR"   ~ "CSpR",
      "CSplusNR"  ~ "CSpNR",
      "Csminus"   ~ "CSm",
      "CSplusACQ" ~ "CSpACQ")
  )

# Calculate SCR means, splitting EXT into EXT1 and EXT2
scr_split_means <- scr_long %>%
  mutate(Phase = case_when(
    Phase == "EXT" & Trial <= 6  ~ "EXT1",
    Phase == "EXT" & Trial > 6   ~ "EXT2",
    TRUE                         ~ Phase  # Keep all other phases as they are
  )) %>%
  group_by(pID, Phase, CS_Type) %>%
  summarize(SCR = mean(SCR_Score, na.rm = TRUE), .groups = "drop")

# Merge all data (keeping only EXT2 of SCR data)
scr_for_merge <- scr_split_means %>%
  # Remove EXT1 as we are focusing on Late Extinction
  filter(Phase != "EXT1") %>%
  # Rename EXT2 to EXT so it matches the "Phase" column in MRI/Ratings
  mutate(Phase = if_else(Phase == "EXT2", "EXT", Phase))

# Master Merge
master_data <- gppi_clean %>%
  full_join(ratings_long, by = c("pID", "Phase", "CS_Type")) %>%
  full_join(scr_for_merge, by = c("pID", "Phase", "CS_Type"))

# Set correct order of factor levels
master_data <- master_data %>%
  mutate(
    # Reorder Phase chronologically
    Phase = fct_relevel(Phase, "ACQ", "REACT", "EXT", "EXTRE", "REN"),
    
    # Reorder CS Type
    CS_Type = fct_relevel(CS_Type, "CSpR", "CSpNR", "CSm", "CSpACQ")
  )

# Save master data
write_csv(master_data,"../data/processed/master_data.csv")

```

## Raw Data Plots {.tabset .tabset-pills}

```{r plot_raw_data, results='asis'}

# ---------------
# Plot Ratings
# ---------------

# Add info for tabs
cat("\n### Ratings (Raw data)\n")

# Make plot
ggplot(master_data, aes(x = Phase, y = Rating, fill = CS_Type)) +
  geom_boxplot(alpha = 0.7) +
  theme_minimal() +
  labs(title = "Expectancy Ratings by Phase and CS Type",
       y = "US-expectancy",
       x = "Phase") +
  scale_fill_brewer(palette = "Set1")

# Add info for tabs
cat("\n")

# ---------------
# Plot SCR
# ---------------

# Add info for tabs
cat("\n### SCR (Raw data)\n")

# Make plot
ggplot(master_data, aes(x = Phase, y = SCR, fill = CS_Type)) +
  geom_boxplot(alpha = 0.7) +
  theme_minimal() +
  labs(title = "Average SCR by Phase and CS Type",
       y = "SCR (z-score)",
       x = "Phase") +
  scale_fill_brewer(palette = "Set1")

# Add info for tabs
cat("\n")

# ---------------
# Plot gPPI
# ---------------

conn_names <- master_data %>% 
  select(contains("Connection")) %>% 
  colnames()

for (conn in conn_names) {
  
  # Add info for tabs
  cat("\n###", conn_dict[conn], "\n")
  
  # Make plot
  p <- ggplot(master_data, aes(x = Phase, y = .data[[conn]], fill = CS_Type)) +
    geom_boxplot(alpha = 0.7, outlier.shape = NA) +
    geom_jitter(position = position_jitterdodge(), alpha = 0.3, size = 1) +
    theme_minimal() +
    labs(title = paste("Connection:", conn_dict[conn]),
         y = "gPPI Parameter Estimate", x = "Phase") +
    scale_fill_brewer(palette = "Set1")
  
  # Print plot
  print(p)
  
  # Add info for tabs
  cat("\n")
}

```

## {-}

## Data cleaning
- Remove outliers (>4 SD)

```{r data_cleaning, message=TRUE}

# -------------------------
# Outlier removal function
# -------------------------

clean_outliers <- function(data_to_clean, var_name, thresh) {
  
  # New column name string
  new_col_name <- paste0(var_name, "_cleaned")
  
  # Remove the outliers
  data_cleaned <- data_to_clean %>%
    group_by(Phase, CS_Type) %>%
    mutate(
      var_Mean = mean(.data[[var_name]], na.rm = TRUE),
      var_SD   = sd(.data[[var_name]], na.rm = TRUE),
      is_outlier = abs(.data[[var_name]] - var_Mean) > (thresh * var_SD)
    ) %>%
    mutate(
      !!new_col_name := if_else(is_outlier, NA_real_, .data[[var_name]])
    ) %>%
    ungroup()
  
  # Outlier stats
  
  outlier_count <- sum(data_cleaned$is_outlier, na.rm = TRUE)
  # Calculate % based on the original column
  non_na_count <- sum(!is.na(data_to_clean[[var_name]]))
  outlier_pct <- (outlier_count / non_na_count) * 100

  cleaning_log <- data.frame(
    Variable = var_name,
    Outliers_N = outlier_count,
    Outliers_Pct = paste0(round(outlier_pct, 2), "%"),
    stringsAsFactors = FALSE
  )
  
  return(list(data = data_cleaned, log = cleaning_log))
}
  
# -------------------------
# Data to clean
# -------------------------

all_logs <- list()

# SCR
outlier_result    <- clean_outliers(scr_long, "SCR_Score", 4)
scr_long_cleaned  <- outlier_result$data
all_logs[["SCR"]] <- outlier_result$log

# gPPI
for (conn in conn_names) {
  outlier_result   <- clean_outliers(gppi_clean, conn, 4)
  gppi_clean       <- outlier_result$data
  all_logs[[conn]] <- outlier_result$log
}

# Display outlier log table
summary_log_table <- bind_rows(all_logs)
knitr::kable(summary_log_table, 
             caption = "Data Quality Report: Outlier Removal Summary (Mean +/- 4 SD)",
             col.names = c("Connection", "N Removed", "% of Data"))

# --------------------------------------
# Add clean data back into master data
# --------------------------------------

# Calculate SCR means, splitting EXT into EXT1 and EXT2
scr_split_means_cleaned <- scr_long_cleaned %>%
  mutate(Phase = case_when(
    Phase == "EXT" & Trial <= 6  ~ "EXT1",
    Phase == "EXT" & Trial > 6   ~ "EXT2",
    TRUE                         ~ Phase  # Keep all other phases as they are
  )) %>%
  group_by(pID, Phase, CS_Type) %>%
  summarize(SCR = mean(SCR_Score_cleaned, na.rm = TRUE), .groups = "drop")

# Prep merge: SCR data (EXT2)
scr_for_merge_cleaned <- scr_split_means_cleaned %>%
  # Remove EXT1 as we are focusing on Late Extinction
  filter(Phase != "EXT1") %>%
  # Rename EXT2 to EXT so it matches the "Phase" column in MRI/Ratings
  mutate(Phase = if_else(Phase == "EXT2", "EXT", Phase))

# Prep merge: gPPI data
gppi_for_merge <- gppi_clean %>%
  select(pID, Phase, CS_Type, ends_with("_cleaned")) %>%
  rename_with(~ str_remove(.x, "_cleaned"), ends_with("_cleaned"))

# Master Merge
master_data_cleaned <- gppi_for_merge %>%
  full_join(ratings_long, by = c("pID", "Phase", "CS_Type")) %>%
  full_join(scr_for_merge_cleaned, by = c("pID", "Phase", "CS_Type")) %>%
  mutate(
    # Set correct order of factor levels
    Phase = fct_relevel(Phase, "ACQ", "REACT", "EXT", "EXTRE", "REN"),
    CS_Type = fct_relevel(CS_Type, "CSpR", "CSpNR", "CSm", "CSpACQ")
  )

# Save cleaned data
write_csv(master_data_cleaned,"../data/processed/master_data_cleaned.csv")

```

# Descriptives

```{r descriptives_table}

# Prep data for summary statistics
master_data_cleaned_long <- master_data_cleaned %>%
  pivot_longer(
    cols = c(Rating, SCR, contains("Connection")),
    names_to = "Measure_ID",
    values_to = "Value"
  ) %>%
  # Add connection labels using the dictionary
  mutate(Measure_Label = case_when(
    Measure_ID == "Rating"           ~ "US-Expectancy Rating",
    Measure_ID == "SCR" ~ "Skin Conductance Response (z-score)",
    Measure_ID %in% names(conn_dict) ~ conn_dict[Measure_ID],
    TRUE                            ~ Measure_ID
  )) %>%
  mutate(as.factor(Measure_Label)) %>%
  mutate(as.factor(Measure_ID)) %>%
  mutate(
    Phase = fct_relevel(Phase, "ACQ", "REACT", "EXT", "EXTRE", "REN"),
    CS_Type = fct_relevel(CS_Type, "CSpR", "CSpNR", "CSm", "CSpACQ")
  )

# Calculate summary statistics
descriptive_stats <- master_data_cleaned_long %>%
  group_by(Measure_Label, Measure_ID, Phase, CS_Type) %>%
  summarise(
    Mean = mean(Value, na.rm = TRUE),
    SD   = sd(Value, na.rm = TRUE),
    N    = sum(!is.na(Value)),
    SE   = SD / sqrt(N),
    .groups = "drop"
  )

# View the descriptives table
descriptive_stats %>% 
  mutate(across(where(is.numeric), ~round(.x, 3))) %>% 
  DT::datatable(options = list(pageLength = 20, scrollX = TRUE))

# Save the descriptives table
write_csv(master_data_cleaned,"../output/tables/descriptive_stats.csv")


```

## Clean Data Plots {.tabset .tabset-pills}

```{r descriptives_plots, results='asis'}

# ------------------
# Plot function
# ------------------

descriptives_plot <- function(data, title_label, y_axis_text) {
  
  # Calculate y min and max so x-axis can cross at bottom (not 0)
  y_min <- min(data$Mean - data$SE, na.rm = TRUE)
  y_max <- max(data$Mean + data$SE, na.rm = TRUE)

  # Reset ymin to be 0 (for plotting purposes)
  if (y_min < 0) {
    data <- data %>% 
      mutate(
        Mean_plot = Mean + abs(y_min),
        SE_lower_plot = (Mean - SE) + abs(y_min),
        SE_upper_plot = (Mean + SE) + abs(y_min)
      )
  } else {
    data <- data %>% 
    mutate(
      Mean_plot = Mean,
      SE_lower_plot = (Mean - SE),
      SE_upper_plot = (Mean + SE)
      )
  }
  
  # Plot the data
  ggplot(data, aes(x = Phase, y = Mean_plot, fill = CS_Type)) +
    geom_bar(stat = "identity", position = position_dodge(0.9), color = "black", size = 0.3) +
    geom_errorbar(aes(ymin = SE_lower_plot, ymax = SE_upper_plot), 
                  width = 0.2, position = position_dodge(0.9)) +
    scale_y_continuous(
      expand = c(0, 0),
      labels = function(x) round(x + y_min, 3)
    ) +
    theme_minimal() +
    labs(title = title_label, y = y_axis_text, x = "Phase") +
    scale_fill_brewer(palette = "Set1") +
    theme(legend.position = "right")
}

# ------------------
# Ratings
# ------------------

# Add info for tabs
cat("\n### Ratings \n")

rating_data_plot <- descriptive_stats %>% filter(Measure_ID == "Rating")
descriptives_plot(rating_data_plot, "US-Expectancy Ratings (Mean +- SE)", "US-Expectancy (0-10)")

# Add info for tabs
cat("\n")

# ------------------
# SCR
# ------------------

# Add info for tabs
cat("\n### SCR (Clean data)\n")

scr_data_plot <- descriptive_stats %>% filter(Measure_ID == "SCR")
descriptives_plot(scr_data_plot, "Skin Conductance Responses (Mean +- SE)", "SCR (z-score)")

# Add info for tabs
cat("\n")

# ------------------
# gPPI
# connections that are p-FDR < 0.05 for main effect across all CS types and Phases
# ------------------

significant_conn_ids <- gppi_metadata %>%
  mutate(`p-FDR` = as.numeric(`p-FDR`)) %>%
  filter(`p-FDR` < 0.05) %>%
  pull(Connection)

for (id in significant_conn_ids) {
  full_name <- conn_dict[id] 
  
  # Add info for tabs
  cat("\n###", full_name, "\n")
  
  conn_data_plot <- descriptive_stats %>% filter(Measure_ID == id)
  print(descriptives_plot(conn_data_plot, paste0(full_name, " (Mean +- SE)"), "gPPI Parameter Estimate"))
  
  # Add info for tabs
  cat("\n")

}

```
## {-}

# Analysis

## Research Question 1:

Are there differences between the reactivated versus non-reactivated CS+

**Models tested**

- H1: CS- = CS+R = CS+NR [Null hypothesis]

- H2: CS- = CS+R < CS+NR [Experimental hypothesis (A)]

- H3: CS- < CS+R < CS+NR [Experimental hypothesis (B)]

- H4: CS- < CS+R = CS+NR [Alternative hypothesis]


**BAIN settings**

Fraction=3: A "medium" wide prior, justified given sample size (N=29)


*Results table shows BF and PMP for models tested against the unconstrained hypothesis*


```{r analysis_rq1}

# Define variables to be tested
analysis_vars <- c("Rating", "SCR", significant_conn_ids)

# Define the Models to be tested
models <- "CS_TypeCSm = CS_TypeCSpR = CS_TypeCSpNR; 
           CS_TypeCSm = CS_TypeCSpR < CS_TypeCSpNR; 
           CS_TypeCSm < CS_TypeCSpR < CS_TypeCSpNR; 
           CS_TypeCSm < CS_TypeCSpR = CS_TypeCSpNR"

# Create a function to run BAIN
run_bain <- function(var_name, phase_name, data) {
  
  # Filter for phase
  analysis_data <- data %>% filter(Phase == phase_name)
  
  # Fit the model
  f <- as.formula(paste(var_name, "~ CS_Type - 1"))
  fit <- lm(f, analysis_data)
  fit$call$formula <- f
  
  # Run BAIN
  res <- bain(fit, models, fraction = 3)
  
  # Extract BFu (Bayes Factor vs Unconstrained)
  # and PMPb (Posterior Model Probability - including unconstrained)
  results <- data.frame(
    Variable = var_name,
    Category = cat_dict[var_name],
    Phase = phase_name,
    Hypothesis = paste0("H", 1:4),
    BFu = res$fit$BF.u[1:4],
    PMPb = res$fit$PMPb[1:4]
  )

  return(results)
}

# Loop through Phases and Variables
all_bain_results <- list()

for (ph in c("EXT", "EXT-RE", "REN")) {
  for (v in analysis_vars) {
    all_bain_results[[paste(ph, v)]] <- run_bain(v, ph, master_data_cleaned)
  }
}

# Combine into one Results Table
bain_summary_long <- bind_rows(all_bain_results) %>%
  mutate(
    # Use the dictionary to get pretty names for the table
    Label = case_when(
      Variable == "Rating"           ~ "US-Expectancy",
      Variable == "SCR"              ~ "SCR",
      Variable %in% names(conn_dict) ~ conn_dict[Variable],
      TRUE                           ~ Variable
    ),
    # Create a combined string column "BFu (PMPb)" for the table cells
    Value_Display = paste0(round(BFu, 2), " (", round(PMPb, 3), ")")
  )

# Pivot to Wide Format (4 columns for 4 Hypotheses)
bain_final_table <- bain_summary_long %>%
  select(Phase, Label, Category, Hypothesis, Value_Display) %>%
  pivot_wider(names_from = Hypothesis, values_from = Value_Display) %>%
  arrange(Phase, Label)

# Display in scrollable format
bain_final_table %>% 
  DT::datatable(options = list(pageLength = 27, scrollX = TRUE))

# Save in output folder
write_csv(bain_final_table, "../output/tables/RQ1_Bayesian_Hypothesis_Results.csv")

```


```{r analysis_rq1_visuals}

# Identify the 'Winning' model for every test
winning_results <- bain_summary_long %>%
  group_by(Phase, Variable) %>%
  slice_max(PMPb, n = 1, with_ties = FALSE) %>%
  left_join(gppi_metadata, by = c("Variable" = "Connection")) %>%
  mutate(
    # Set correct order of factor levels
    Category.x = fct_relevel(Category.x, "Self-report", "Physiology", "vmPFC-Amygdala", "Amygdala-vmPFC", "Intra-amygdala","Intra-vmPFC")
    )

# Plot the Heatmap
plot_heatmap <- ggplot(winning_results, aes(x = Phase, y = Label, fill = Hypothesis)) +
  geom_tile(aes(alpha = PMPb), color = "white") +
  facet_grid(Category.x ~ ., scales = "free_y", space = "free_y") +
  scale_fill_brewer(palette = "Set2") +
  theme_minimal() +
  labs(title = "Winning model by variable and phase",
       subtitle = "Intensity represents PMP",
       fill = "Winning Model") +
  theme(axis.text.y = element_text(size = 8),
        strip.text.y = element_text(angle = 0, face = "bold", hjust = 0))

# Save the heatmap
ggsave("../output/figures/RQ1_BAIN_heatmap.png", plot_heatmap)
  

```


## Research Question 2:
Does connectivity strength relate to SCR?


SCR and gPPI responses to CS- were subtracted from responses to CS+R and CS+NR. \n
We then tested if gPPI responses for CS+R and CS+NR (CS- adjusted) could predict SCR (CS- adjusted) responses. \n
The **main effect** results indicate if gPPI predicts SCR (irrespective of CS Type),\n
the **interaction effect** results indicate if the relationship between gPPI and SCR differed for CS+R and CS+NR.


Conducted linear models of the form:

SCR ~ gPPI * CS Type - 1


*FDR adjusted p-values calculated per phase (NB: No test survive FDR correction)*

```{r analysis_rq2}

# ----------------------------
# Create a function to run lm
# ----------------------------
run_analysis_rq2 <- function(var_name, phase_name, data) {
  
  # Filter for phase
  analysis_data <- data %>% 
    filter(Phase == phase_name)
  
  # Fit the model
  f       <- as.formula(paste("SCR_delta ~ 1 + CS_Type * ", var_name))
  fit     <- lm(f, analysis_data)
  s       <- summary(fit)
  slopes  <- as.data.frame(emtrends(fit, ~ CS_Type, var = var_name))
  
  # Get the interaction term p-value and beta from the model summary
  int_p <- tidy(s) %>% 
    filter(grepl(":", term)) %>% 
    pull(p.value)
  int_b <- tidy(s) %>% 
    filter(grepl(":", term)) %>% 
    pull(estimate)
  
  # Get the effect of gPPI on SCR from the model summary
  main_effect <- as.data.frame(test(emtrends(fit, ~ 1, var = var_name)))

  # Extract results
  results_rq2 <- data.frame(
    Variable = var_name,
    Variable_name = conn_dict[str_remove(var_name, "_delta")],
    Variable_category = cat_dict[str_remove(var_name, "_delta")],
    Phase = phase_name,
    MainEffect_B = main_effect[1,2],
    MainEffect_p = main_effect[1,6],
    Slope_CSpR = slopes[slopes$CS_Type == "R", 2], # The trend column
    Slope_CSpNR = slopes[slopes$CS_Type == "NR", 2],
    Interaction_B = int_b,
    Interaction_p = int_p
  )

  return(results_rq2)
}

# ----------------------------
# Prepare the data
# ----------------------------

# Create a Wide dataframe to calculate responses minus CS-
delta_analysis_data <- master_data_cleaned %>%
  # Select only the variables needed
  select(pID, Phase, CS_Type, SCR, all_of(significant_conn_ids)) %>%
  # Pivot so each CS_Type gets its own column for every measure
  pivot_wider(
    names_from = CS_Type,
    values_from = c(SCR, all_of(significant_conn_ids))
  ) %>%
  # Calculate SCR Deltas (CSplus minus CSminus)
  mutate(
    SCR_delta_R  = SCR_CSpR - SCR_CSm,
    SCR_delta_NR = SCR_CSpNR - SCR_CSm
  )

# Calculate deltas for all significant connections
for (conn in significant_conn_ids) {
  col_R  <- paste0(conn, "_CSpR")
  col_NR <- paste0(conn, "_CSpNR")
  col_M  <- paste0(conn, "_CSm")
  
  delta_analysis_data[[paste0(conn, "_delta_R")]]  <- delta_analysis_data[[col_R]] - delta_analysis_data[[col_M]]
  delta_analysis_data[[paste0(conn, "_delta_NR")]] <- delta_analysis_data[[col_NR]] - delta_analysis_data[[col_M]]
}

# Then convert back to long form for analysis
delta_names <- delta_analysis_data %>% 
  select(contains("delta")) %>% 
  colnames()

delta_analysis_data <- delta_analysis_data %>%
  # Select only the variables needed
  select(pID, Phase, delta_names) %>%
  # Pivot to Long form
  pivot_longer(
    cols = delta_names, 
    names_to = c(".value", "CS_Type"), 
    names_pattern = "(.*_delta)_(.*)"
  )

# ----------------------------
# Prepare the analysis
# ----------------------------

# Define variables to be tested
analysis_vars <- delta_analysis_data %>% 
  select(contains("Connection")) %>% 
  colnames()

# Loop through Phases and Variables
all_rq2_results <- list()

for (ph in c("EXT", "EXT-RE", "REN")) {
  for (v in analysis_vars) {
    all_rq2_results[[paste(ph, v)]] <- run_analysis_rq2(v, ph, delta_analysis_data)
  }
}

# Combine the results list into one master dataframe
rq2_summary_table <- bind_rows(all_rq2_results) %>%
  # Perform FDR correction per phase (accounting for 25 tests per phase)
  group_by(Phase) %>%
  mutate(
    # Use Benjamini-Hochberg (FDR) correction
    Interaction_p_FDR = p.adjust(Interaction_p, method = "fdr"),
    MainEffect_p_FDR = p.adjust(MainEffect_p, method = "fdr"),
    
    # Add significance flags
    Significance = case_when(
      Interaction_p < 0.05 ~ "Interaction *",
      MainEffect_p < 0.05  ~ "Main Effect *",
      TRUE ~ "n.s."),
    Signifcance_FDR = case_when(
      Interaction_p_FDR < 0.05 ~ "Interaction *",
      MainEffect_p_FDR < 0.05 ~ "Main Effect *",
      TRUE ~ "n.s.")
  ) %>%
  ungroup() %>%
  # Clean up the numbers
  mutate(
    across(where(is.numeric), ~ round(.x, 3))
  )

# Display in scrollable format
rq2_summary_table %>% 
  DT::datatable(options = list(pageLength = 25, scrollX = TRUE))

# Save the table in output folder
write_csv(master_data_cleaned,"../output/tables/RQ2_Linear_Models_Results.csv")

```


```{r analysis_rq2_visuals}

# ---------------------
# Forest plot function
# ---------------------

RQ2_plots <- function(data_table, x_data, sig_flag, sig_color, title) {
  
  p <- ggplot(data_table, aes(x = x_data, y = reorder(Variable_name, x_data))) +
    
    geom_vline(xintercept = 0, linetype = "dotted", color = "gray50") +
    
    geom_segment(aes(x = 0, xend = x_data, yend = Variable_name, color = sig_flag), size = 0.8) +
    geom_point(aes(color = sig_flag), size = 2.5) +
    
    facet_grid(Variable_category ~ Phase, scales = "free_y", space = "free_y") +
    
    scale_color_manual(values = c("TRUE" = sig_color, "FALSE" = "gray80")) +
    scale_alpha_manual(values = c("TRUE" = 1, "FALSE" = 0.4)) +
    theme_minimal() +
    theme(
      strip.text.y = element_text(angle = 0, face = "bold"), # Keep category names horizontal
      strip.background = element_rect(fill = "gray95", color = NA),
      axis.text.y = element_text(size = 7),
      panel.spacing = unit(1, "lines")
    ) +
    labs(
      title = title,
      x = "Estimate",
      y = "",
      color = "p < .05"
    )
  
  return(p)
  
}


# Signifcance flags for plotting
rq2_summary_table <- rq2_summary_table %>%
  mutate(
    is_sig_int = (Interaction_p < 0.05),
    is_sig_me = (MainEffect_p < 0.05)
  )

plot_forest_int <- RQ2_plots(rq2_summary_table, rq2_summary_table$Interaction_B, rq2_summary_table$is_sig_int, "red", "CS Type X gPPI interaction effects on SCR")
plot_forest_me <- RQ2_plots(rq2_summary_table, rq2_summary_table$MainEffect_B, rq2_summary_table$is_sig_me, "blue", "Main effect of gPPI on SCR")

# Save the forest plots
plot_forest_int
ggsave("../output/figures/RQ2_Forestplot_interaction.png", plot_forest_int)
plot_forest_me
ggsave("../output/figures/RQ2_Forestplot_maineffect.png", plot_forest_me)

```